Lessons Learned from Differential Testing JS Engines

### 2018-07-05 paper/paper.tex
pass

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cycle icons denote repetition--the leftmost icon
indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon indicates that a single file will be
processed multiple times in fuzzing mode. The bug-finding process
takes on input JS files from regression test suites of various JS
engines.

The bug-finding process works as follows.  Considering the case
fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output produced
for that file is consistent across all engine implementations. In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure discards the corresponding
input (mark ....). Otherwise, it considers the input as potentially
fault-revealing; hence interesting for human inspection. Considering
the case where fuzzing~\cite{fuzz-testing-history} is selected, new
inputs are obtained from a given input using some off-the-shelf
fuzzer\footnote{Several fuzzing methods have been proposed in the
  past, varying with respect to how new inputs are generated (\eg{},
  coverage-based~\cite{afl,honggfuzz},
  grammar-based~\cite{grammarinator,jsfunfuzz}, and
  random-based~\cite{radamsa}).}. The workflow is similar to that of
no fuzzing. In this case, however, multiple warnings can be produced
for a given seed input.

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. The HI
group includes those inputs where execution manifests anomaly during
the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}. The rationale is that
the test in this group executed without violating any internal checks
of the API.  The LO group, in contrast, includes those cases where the
anomaly was observed during the execution of some API function. We
found that engine implementations often check pre-conditions of API
functions differently. It can happen, for example, that one engine
enforces a pre-condition that another engine does not. In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO and provide the rationale for such classification.}
\Mar{can we detect dups mining issue trackers?}

@@

Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
used.\Mar{identify sources assoc. with the four analyzed engines.} The results of this query is sorted in descending order of
stars. Initially, we obtained a total of \Fix{XX} projects. Manually,
we follow the criteria to exclude invalid projects and we obtained a
total of \Fix{XX} repositories. Table~\ref{tab:test-suites} shows the
JS sources we considered. Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these names}

\begin{table}[h]
  \centering
  \caption{\label{tab:test-suites}Test Suites}
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \cite{duktape} & 997 \\
    JerryJS & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\
    Mozilla & \Fix{??} & 32,414 \\
    V8.test.benchmarks.data & \Fix{??} & 64 \\
    WebKit.jstests.es6 & \Fix{??} & 605 \\
    WebKit.jstests.microbenchmarks & \Fix{??} & 426 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

\begin{figure}
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
  }
\end{figure}

It is worth noting that many projects use distinct frameworks for
testing and require external libraries to run their testing
suites. For some projects, we made small changes in the testing
infrastructure to be able to uniformly run the test in all
engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}We aimed to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

@@

\subsection{Fuzzers}

>>>>

Figure~\ref{fig:workflow} illustrates the infrastructure we used in
this study.
The bug-finding process
takes on input JS files from regression test suites of various JS
engines and generates warnings on output. Boxes in the figure denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cycle icons denote repetition--the leftmost icon
indicates that each file in the input list will be analyzed in
separate whereas the rightmost icon shows that a single file will be
fuzzed multiple times. The bug-finding process works as follows.  Considering the case
where fuzzing is not selected, as illustrated in the inner box at the bottom
of the figure, the oracle checks whether or not the output produced
for that file is consistent across all engine implementations. In case
the test passes in all engines or fails in all engines (\ie{}, the
output is consistent), the infrastructure discards the corresponding
input. Otherwise, it considers the input as potentially
fault-revealing; hence interesting for human inspection. Considering
the case where fuzzing~\cite{fuzz-testing-history} is selected, new
inputs are obtained from a given input using some off-the-shelf
fuzzer. Several fuzzing methods have been proposed in the
  past, varying with respect to how new inputs are generated (\eg{},
  coverage-based~\cite{afl,honggfuzz},
  grammar-based~\cite{grammarinator,jsfunfuzz}, and
  random-based~\cite{radamsa}). Section~\ref{sec:objects:fuzzers} describes the
  fuzzers we selected. The workflow of the infrastructure with fuzzing
  enabled is similar to that of no fuzzing. In this case, however, multiple warnings can be produced
for a given seed input.

The infrastructure outputs a list of warnings for human inspection.
To reduce the number of false alarms, we clustered warnings in two
groups, reflecting their likelihood to manifest a real bug. Warnings
in the HI group are associated with the cases when the anomaly has been
detected during the execution of the test code or its close neighborhood\Comment{ as
  opposed to that of some internal JS function}. The rationale is that
the test in this group executed without violating any internal checks
of the API. In constrast, warnings in the LO group reflect the cases where the
anomaly was observed during the execution of some standard JS
function\Mar{is this correct? what are those?}. We
found that different engines often check the pre-conditions of those
functions differently. It can happen, for example, that one engine
enforces a pre-condition that another engine does not\Mar{why is that?
that should not happen if the spec was fully documented and engines
properly implemented those checks. Explain and give example.}. In those cases,
our infrastructure would observe a discrepancy that is more likely to
be associated with a bug in the (fuzzed) test; not the code. Although
we did find real bugs from warnings in the LO group, the proportion
was much lower compared to the HI group--only 12\% of the reals bugs
we found originated from the LO category. \Mar{show real examples of
  HI and LO.}
\Mar{can we detect dups mining issue trackers?}

@@

Figure~\ref{fig:query} illustrates the Github API query\Fix{cite} we
used to find projects with JS files\Mar{why the query is so specific?
  as per ``q=javascript-engine''? Need to be consistent to what you
  are saying an coherent to what you actually did.}. The query sorts
results in descending order in the number of stars\Mar{sorting is only
  relevant if you set a limit on the number of projects you will
  analyze. What limit is that?}. The resulting list includes a total
of \Fix{XX} projects. A total of \Fix{...}  projects remained after
removing projects that \Fix{...}. Table~\ref{tab:test-suites} shows
the JS sources we considered for each of these selected
projects..\Mar{identify the sources assoc. with the four analyzed
  engines. you said in the first sentence this is one source.} Overall, we found a total of \totfiles{} JS
files.\Mar{Briefly explain these sources.}

\begin{figure}[h]
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contain over 1K stars.\Fix{fix query}
  }
\end{figure}

\begin{table}[t]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Mar{try to use a single
      name (if possible) to facilitate reference in the paper. Use the
  full path in the URL (citation) to indicate where one can find those
  files.}}
  \begin{tabular}{ccr}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \cite{duktape} & 997 \\
    JerryJS & \cite{jerryscript} & 1,803 \\
    JSI & \cite{jsi} & 99 \\
    Tiny-js & \cite{tinyjs} & 44 \\
    Mozilla & \Fix{??} & 32,414 \\
    V8.test.benchmarks.data & \Fix{??} & 64 \\
    WebKit.jstests.es6 & \Fix{??} & 605 \\
    WebKit.jstests.microbenchmarks & \Fix{??} & 426 \\
    \midrule
     &  & 36,452 \\
   \bottomrule     
  \end{tabular}
\end{table}

It is worth noting that some projects use distinct frameworks for
testing and require external libraries to run their testing
suites. For these projects, we needed to make small changes in the testing
infrastructure to be able to uniformly run tests in all
engines.\Mar{not entirely clear what you did to support
  this.$\rightarrow$}We aimed to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion
function that throws an Error that we can capture by our
infraestruture.

@@

\subsection{Fuzzers}
\label{sec:objects:fuzzers}
